Output Summary

### 2023-08-17 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Improve capacity vs. WUL Rmd section

# Parr Capacity vs. Habitat Relationship {.tabset .tabset-pills}

## Scatterplot

Error bars represent the central 80% of the posterior. The many grey lines are individual posterior draws.

@@

## Slope Parameter

```{r beta-v-habitat-slope}
# extract posterior summary of slope
est = post_summ(post, "^lambda$")
colnames(est) = "slope"

>>>>

# Parr Capacity vs. Habitat Relationship

Error bars represent the central 80% of the posterior; grey lines are individual posterior draws of the expected relationship.

@@

```{r beta-v-habitat-slope}
# extract posterior summary of slope
est = post_summ(post, "^lambda$")
colnames(est) = "Slope"
